Hypertension and microbiome

### 2019-04-29 articletwo.Rmd
Duplicated label

```{r Write figure 3}
fig3head <- "Associations between genus level abundances and blood pressure variables"
fig3foot <- "Only backteria with significant associations are shown. Blood pressure variables are normalized and abundances are arcsin-square root transformed. Dark gray color represents unsignificant associations."
writeimage(doc, 3, "cache/maaslin.png", fig3head, fig3foot)
```

>>>>

```{r Write figure 4}
fig3head <- "Associations between genus level abundances and blood pressure variables"
fig3foot <- "Only backteria with significant associations are shown. Blood pressure variables are normalized and abundances are arcsin-square root transformed. Dark gray color represents unsignificant associations."
writeimage(doc, 3, "cache/maaslin.png", fig3head, fig3foot)
```
